Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-03-24 MUSES_vs_BYOD_solutions.tex
Metiendo referencias en el bib
Van un puñao.
Sigo adelante.

The other issue to cope with is the elaboration of a good ISP, understandable for every user of the company, and more importantly, non-intrusive for him. A lot of researchers have studied the natural tendency of employees to comply with the ISP \cite{SecPolComp07,SecPolComp10,SecPolComp12}, reaching conclusions such as the employees compliance with the security policies increases educating/training them in information security awareness  \cite{SecPolComp09}, and decreases applying too much sanctions when a misuse or abuse occurs \cite{SecPolPenalty09}. Thus, in this paper, for each tool in Section \ref{sec:toolsreview} it is specified if the developers have taken into account the construction of ISPs, or even if they give some guidelines for building them.

@@

\bibitem{android11}
Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}. MobiSec Session on Smartphone Security, Aalborg 2011.

\bibitem{BigData_11}
Ratner, B.:
\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.

\bibitem{policy_generation_clustering_10}
Samak, T. and Al-Shaer, E.:
\newblock Synthetic security policy generation via network traffic clustering.
\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
  ACM.

\bibitem{Samsung_tool}
Samsung KNOX.
\newblock
  \url{https://www.samsungknox.com}

\bibitem{Schu_SecPatterns05}
Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
  Sommerlad, P.:
\newblock {\em Security Patterns: Integrating Security and Systems
  Engineering}.
\newblock John Wiley \& sons, 2005.

\bibitem{RT2AE_SOTICS13}
Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
\newblock A survey of trust and risk metrics for a BYOD mobile working world.
\newblock In {\em Third International Conference on Social Eco-Informatics
  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.

\bibitem{SecPolComp09}
Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.

\bibitem{SecPolComp07}
Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}. In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp. 133-144, 2007.

\bibitem{AAI_book_2009}
Solanas, A. and Martínez-bal, A.:
\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
  Security}.
\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.

\bibitem{Sophos_tool}
Sophos.
\newblock Mobile control.
\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}

\bibitem{rule_generation_gp_09}
Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
\newblock Automatic rule generation based on genetic programming for event
  correlation.
\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
  Computational Intelligence in Security for Information Systems}, volume~63 of
  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
  Berlin Heidelberg, 2009.

\bibitem{risk_reduction_ga_12}
Tamjidyamcholo, A.:
\newblock Genetic algorithm approach for risk reduction of information
  security.
\newblock {\em International Journal of Cyber-Security and Digital Forensics
  (IJCSDF)}, 1(1), 2012.

\bibitem{SurveyEventCorrelation_Tiffany02}
Tiffany, M.:
\newblock A survey of event correlation techniques and related topics.
\newblock Research paper, Georgia Institute of Technology, 2002.

\bibitem{WorxSDK}
Citrix.
\newblock Worx App SDK.
\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}

\bibitem{WSO2_tool}
WSO2.
\newblock Enterprise Mobility Manager.
\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}

\bibitem{GA_networksecurity-zarza} 
Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358. World Scientific, 2010.

\bibitem{GA_cryptographicprotocols-zarza2} 
Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques. In M. Malek, E. Fernández-Medina, and J. Hernando, editors, SECRYPT, pages 316-319. INSTICC Press, 2006.

>>>>

The other issue to cope with is the elaboration of a good ISP, understandable for every user of the company, and more importantly, non-intrusive for him. A lot of researchers have studied the natural tendency of employees to comply with the ISP \cite{SecPolComp10,SecPolComp12,SecPolComp14}, reaching conclusions such as the employees compliance with the security policies increases educating/training them in information security awareness  \cite{SecPolComp09}, and decreases applying too much sanctions when a misuse or abuse occurs \cite{SecPolPenalty09}. Thus, in this paper, for each tool in Section \ref{sec:toolsreview} it is specified if the developers have taken into account the construction of ISPs, or even if they give some guidelines for building them.

@@

%\bibitem{android11}
%Orthacker, C., Teufl, P., Kraxberger, S., Lackner, G., Gissing, M., Marsalek, A., Leibetseder, J., and Prevenhueber, O.: \emph{Android Security Permissions - Can We Trust Them?}. MobiSec Session on Smartphone Security, Aalborg 2011.

%\bibitem{BigData_11}
%Ratner, B.:
%\newblock {\em Statistical and Machine-Learning Data Mining: Techniques for
%  Better Predictive Modeling and Analysis of Big Data, Second Edition}.
%\newblock CRC Press, Inc., Boca Raton, FL, USA, 2nd edition, 2011.

%\bibitem{policy_generation_clustering_10}
%Samak, T. and Al-Shaer, E.:
%\newblock Synthetic security policy generation via network traffic clustering.
%\newblock In {\em Proceedings of the 3rd ACM Workshop on Artificial
%  Intelligence and Security}, AISec '10, pages 45--53, New York, NY, USA, 2010.
%  ACM.

%\bibitem{Samsung_tool}
%Samsung KNOX.
%\newblock
%  \url{https://www.samsungknox.com}

%\bibitem{Schu_SecPatterns05}
%Schumacher, M., Fernandez-Buglioni, E., Hybertson, D., Buschmann, F., and
%  Sommerlad, P.:
%\newblock {\em Security Patterns: Integrating Security and Systems
%  Engineering}.
%\newblock John Wiley \& sons, 2005.

%\bibitem{RT2AE_SOTICS13}
%Seigneur, J.-M., Kölndorfer, P., Busch, M., and Hochleitner, C.:
%\newblock A survey of trust and risk metrics for a BYOD mobile working world.
%\newblock In {\em Third International Conference on Social Eco-Informatics
%  (SOTICS 2013)}, page To Appear. Curran Associates Inc., November 2013.

%\bibitem{SecPolComp09}
%Shaw, R.S., Chen, C.C., Harris, A.L., and Huang, H.-J.: \emph{The impact of information richness on information security 
%awareness training effectiveness}. Computers \& Education, vol. 52, pp. 92-100, 2009.

%\bibitem{SecPolComp07}
%Siponen, M., Pahnila, S., and Mahmood, A.: \emph{Employees' adherence to information security policies: an empirical study}. In IFIP International Federation for Information Processing, Volume 232, New Approaches for Security, Privacy and Trust in Complex Environments pp. 133-144, 2007.

%\bibitem{AAI_book_2009}
%Solanas, A. and Martínez-bal, A.:
%\newblock {\em Advances in Artificial Intelligence for Privacy Protection and
%  Security}.
%\newblock World Scientific Publishing Co., Inc., River Edge, NJ, USA, 2009.

%\bibitem{Sophos_tool}
%Sophos.
%\newblock Mobile control.
%\newblock \url{http://www.sophos.com/en-us/products/mobile-control.aspx}
%
%\bibitem{rule_generation_gp_09}
%Suarez-Tangil, G., Palomar, E. Fuentes, J., Blasco, J. and Ribagorda, A.:
%\newblock Automatic rule generation based on genetic programming for event
%  correlation.
%\newblock In l.~Herrero, P.~Gastaldo, R.~Zunino, and E.~Corchado, editors, {\em
%  Computational Intelligence in Security for Information Systems}, volume~63 of
%  {\em Advances in Intelligent and Soft Computing}, pages 127--134. Springer
%  Berlin Heidelberg, 2009.

%\bibitem{risk_reduction_ga_12}
%Tamjidyamcholo, A.:
%\newblock Genetic algorithm approach for risk reduction of information
%  security.
%\newblock {\em International Journal of Cyber-Security and Digital Forensics
%  (IJCSDF)}, 1(1), 2012.

%\bibitem{SurveyEventCorrelation_Tiffany02}
%Tiffany, M.:
%\newblock A survey of event correlation techniques and related topics.
%\newblock Research paper, Georgia Institute of Technology, 2002.

%\bibitem{WorxSDK}
%Citrix.
%\newblock Worx App SDK.
%\newblock \url{http://www.citrix.es/go/worx-app-sdk.html}
%
%\bibitem{WSO2_tool}
%WSO2.
%\newblock Enterprise Mobility Manager.
%\newblock \url{http://wso2.com/products/enterprise-mobility-manager/}

%\bibitem{GA_networksecurity-zarza} 
%Zarza, L., Forné, J., Pegueroles, J.R., and Soriano, M.: Advances in artificial intelligence for privacy protection and security, chapter Genetic algorithms for designing network security protocols, pages 325-358. World Scientific, 2010.
%
%\bibitem{GA_cryptographicprotocols-zarza2} 
%Zarza, L., Pegueroles, J., Soriano, M., and Martínez, R.: Design of cryptographic protocols by means of genetic algorithms techniques. In M. Malek, E. Fernández-Medina, and J. Hernando, editors, SECRYPT, pages 316-319. INSTICC Press, 2006.
